### 2017-04-11 paper1.tex
Add files via upload

\chapter{A method to correct upwelling longwave radiation to estimate hemispherical urban surface temperature}

\section{Introduction}
Thermal infrared (TIR) remote sensing of land surface temperature (T\textsubscript{surf}) has emerged as a primary research focus in climatology, as researchers seek to better describe spatiotemporal patterns of T\textsubscript{surf} globally and better understand how anthropogenic modification of earth's surface influences land T\textsubscript{surf} with links to the climate at-large. Over the last two decades, use of thermal remote sensing of surface climates has expanded significantly --- both in terms of the volume and breadth of remote sensed study and its explicative importance in climatology as a discipline. Thermal remote sensing of earth's surface has applications over a wide range of disciplines: from informing micro-, urban-, and global-scale climate models, to aiding decision making and mitigation praxis with respect to climate change and the \gls{uhi}.

Within urban climatology, a combination of satellite, aerial, and ground-based thermal remote sensors have been integral in elucidating the spatial \cite{Roth1989}, temporal \cite{Peng2012}, and geometric \cite{Voogt1997} effects of the built environment on land T\textsubscript{surf}; in evaluating and partitioning urban surface energy balances \cite{BastiaanssenW.G.M.1998, Yamaguchi2005} and; in characterizations of the relationship between surface and \gls{blayer} air temperatures (T\textsubscript{air}) \cite{Stoll1992}. These advances have been aided by substantial improvements in sensor ground, spectral, and radiometric resolutions, and by the proliferation of both large-scale public satellite remote sensing campaigns and low-cost aerial and near-ground thermography. However, in spite of it's widespread usage, several questions concerning the use and validity of urban remote thermal remote sensing, first posed in Roth et al. 1989 \cite{Roth1989}, have yet to be sufficiently answered, viz,

@@

\noindent In this paper, we seek to examine question two by introducing and evaluating a method for atmospheric and emissivity correction of near-ground hemispherical TIR --- measured via \gls{pyrg} --- for hemispherical radiometric temperature (T\textsubscript{hem}) retrieval. These measures are common to most urban energy balance assessments and thus constitute a hitherto untapped method for urban T\textsubscript{surf} analysis. A companion paper responds to question one through an analysis of a climatology of T\textsubscript{hem} and derived surface UHI (sUHI), to quantify geometric and temporal biases across multiple methods for remote sensing of urban T\textsubscript{surf}.

@@

Although most thermal remote sensors operate within one of the \gls{atmwind}[s] --- where atmospheric effects are greatly reduced --- virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared \gls{waveband} the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal almost certainly not equal to the ground emitted signal. For an isothermal, homogeneous surface-atmosphere system, at-sensor spectral radiance at height ($z$) can be described by a function deviating from a Planck curve at T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation governed by the difference between Planck curves at T\textsubscript{surf} and the ambient T\textsubscript{air}. As shown for two path geometries in figure \ref{spectairtsurf} for an isothermal atmosphere with water vapor content of 12 \si{\gram\per\meter\cubed} and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere, an at-sensor spectral radiance signal deviates significantly from the surface emitted spectral radiance curve. A less transmissive atmosphere increases the potential for deviation in the at-sensor signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence on the spectral TIR signal.

\begin{figure}[!ht]
	\includegraphics[width=\textwidth]{spectairtsurf}
	\caption{At-sensor spectral directional radiances computed in MODTRAN 4.1 \cite{Berk1987} for short (30 \si{m}) and long (3000 \si{m}) path lengths (z) with Planck curves indicating spectral radiances at T\textsubscript{air} = 305 \si{K} and T\textsubscript{surf} = 295 \si{K}.}
	\label{spectairtsurf}
\end{figure}

Atmospheric effects can lead to differences between the 'true' radiometric T\textsubscript{surf} and the remote sensed T\textsubscript{surf} of over 10 \si{K} for satellite platforms \cite{Cooper1989} and over 6 \si{K} for near-ground sensors \cite{Meier2011}. Moreover, because atmospheric and emissivity effects are a function of non-uniform and spatiotemporally variant surface and atmospheric properties, their associated errors change depending on instrument type, surface-sensor geometry, study location, and ambient conditions. As intersite and time-sequential analysis is a significant goal of most thermal remote sensed studies (urban or otherwise) these effects cannot be ignored.

Spectral transmission of longwave radiation through a given layer of atmosphere is dependent on total column absorber content (the principal broadband TIR absorbers are H\textsubscript{2}0, C0\textsubscript{2}, and to a lesser extent 0\textsubscript{3}, N\textsubscript{2}0, CO, CH\textsubscript{4}, and 0\textsubscript{2} \cite{Miskolczi1993}). Holding vertical absorber content constant, variation in band-by-band TIR transmittance with path length is greatest at urban scales (approximately 1 to 50 \si{m}), where transparent spectral bands can quickly become opaque with small changes in path length or absorber content - illustrated in figure \ref{spectransheight}. Thus, transmittance of TIR near the surface is highly dependent on surface-sensor geometry, instrument spectral response, and atmospheric absorber content. Indeed, accurate assessment of atmospheric influence on TIR may be most complex when measured near the surface.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{spectransheight}
	\caption{Spectral transmission of water vapor as a function of height. Black and grey shading indicate opaque (0\% transmittance) and transparent (100\% transmittance) bands respectively. Redo this figure with wavelength and colorbar no totle and the tick marks in back on the outside?}
	\label{spectransheight}
\end{figure}

Radiation passing through a layer of atmosphere from an emitting surface can be described in a number of ways. \textit{Spectral directional radiance} $ R (\lambda)$, at height $ z $ and from a direction defined by zenith angle \(\theta\), and azimuth angle \(\phi\) is commonly written as

\begin{equation}
R^\uparrow_z (\lambda, \theta, \phi) = \tau_\lambda \epsilon R^\uparrow_0(\lambda) + (1-\epsilon) R^\downarrow_{sky} (\lambda) + (1-\tau_\lambda) R^\uparrow_{atm}(\lambda)
\end{equation}

\noindent where \(\epsilon\) is surface emissivity, \(\tau\)\textsubscript{\( \lambda \)} is spectral "slab" transmittance through the layer between the emitting surface $( z  = 0) $ and $ z $. The same spectral TIR signal, as measured by a narrow-FOV sensor mounted at height $ z $, passes through an instrument shield (or dome) with spectral transmittance \(\tau_d\), and is integrated over the sensor waveband (bounded by \(\lambda_1\) and \(\lambda_2\)) to yield a \textit{directional radiance} $L'$ as 'seen' by the sensor

\begin{equation}
L'_z (\theta, \phi) = \int_{\lambda_1}^{\lambda_2} \tau_d(\lambda) R^\uparrow_z(\lambda) ~ d\lambda
\end{equation}

@@

TIR received by a remote sensor can be related to the emitting body's temperature in a number of ways --- each producing different conceptions of T\textsubscript{surf} from different instrument and sensor types. As such, the term "surface temperature" with respect to a remote sensed TIR is vague and can refer to several definitions of "surface" and "temperature" Thus, proper terminology must be attached to land T\textsubscript{surf} inferred from TIR. Definitions and nomenclature conventions for multiple methods for T\textsubscript{surf} retrieval are discussed at length in Norman \& Becker, (1995)\cite{Norman1995}.

Directional radiance $ L'_z $ detected from a narrow-FOV sensor operating over waveband (\(\lambda_1\) --- \(\lambda_2\)) and viewing the surface from some orientation described by \(\theta\), \(\phi\) can be used to infer a \textit{directional brightness temperature} T'\textsubscript{bright}(\(\theta\), \(\phi\)) via an inversion of the Planck function multiplied by normalized sensor response integrated over the sensor waveband,

\begin{equation}
L'_z(T'_{bright} (\theta, \phi)) = \bigints_{\lambda_1}^{\lambda_2} \cfrac{f(\lambda) C_1}{\pi \lambda^5 \left( \exp\left(\cfrac{C_2}{\lambda T'_{bright} (\theta, \phi)}\right)\right)}
\end{equation}

\noindent where C\textsubscript{1} = $ 3.7404 \cdot 10^8 $ $ W\mu^4 m^{-2} $, C\textsubscript{2} = $ 14387 \mu K $, and relative sensor response $ r(\lambda) $ normalized via,

\begin{equation}
1 ~ =  \int_{\lambda_1}^{\lambda_2} r(\lambda) ~ d\lambda
\end{equation}

Similarly irradiance $L_z$ received by a broadband hemispherical sensor (such as a pyrgeometer), can be used to infer a \textit{hemispherical brightness temperature} T\textsubscript{bright} through an inversion of the Stefan-Boltzmann law,

\begin{equation}
\label{stefb1}
L_z = \overline{r} (\sigma T_{bright}^4)
\end{equation}

@@

\begin{equation}
\overline{r} = \cfrac{\int R(\lambda) ~ r(\lambda)}{\int R(\lambda)}
\end{equation}

\noindent with $ R(\lambda) $ computed from a Planck function at an approximated $T_{bright}$.

In addition, a simple approximation of $T_{bright}$ can be inferred from directional radiance using equation \ref{stefb1} by replacing $ L_z $ with $L'_z$ multiplied by a constant. This method is commonly used to infer T\textsubscript{bright} from infrared thermometers (IRT) operating over the atmospheric window, where atmospheric effects are minimal and T\textsubscript{bright} is a reasonably accurate approximation of T\textsubscript{surf}. However, constants must be calibrated for the range of expected T\textsubscript{surf} as the relationship between $ L_z $ and $L'_z$  is not perfectly linear with respect to emitter temperature.

Inversions of uncorrected $ L_z $ or $L'_z$ yield a temperature equal to that of a blackbody emitting the same amount of radiation as detected by the sensor. Since $ L_z $ ($L'_z$ ) is unlikely to be equal to $ L_0 $ ($L'_0$), T\textsubscript{bright} at $ z = 0 $ and T\textsubscript{bright} at $ z $ often show significant deviation based on sensor characteristics, ambient conditions, and surface-sensor geometry. Hence, remote sensed T\textsubscript{bright} is generally considered only a rough approximation representation of radiometric, kinetic, or thermodynamic T\textsubscript{surf}.

To retrieve a more accurate estimation of the 'true' T\textsubscript{surf}, the same inversions can be applied to TIR measurements after correction for atmospheric and surface emissivity effects (e.g. modification of the remote sensed TIR signal to represent that at $ z = 0 $ of a homogeneous blackbody emitter) to yield a direction radiometric surface temperature  T\textsubscript{rad} for atmospheric and emissivity corrected directional radiances, a hemispherical radiometric surface temperature T\textsubscript{hem} for atmospheric and emissivity corrected irradiances. T\textsubscript{rad} and T\textsubscript{hem} provide a better approximation of the ‘true’ T\textsubscript{surf} by representing the temperature at which the viewed surface is radiating, integrated over the sensor FOV.

@@

A large number of correction routines have been developed to remove atmospheric and emissivity effects from aerial and satellite TIR signals and derive accurate T\textsubscript{rad}. Methods range from simple mono- \cite{Qin2001} and split-window \cite{Wan1996} routines for single- and multi-channel remote sensors to schemes that integrate a radiative transfer code to isolate the surface emitted signal from interfering signals. Boundary conditions are standard across most correction methods: generally requiring vertical profiles of T\textsubscript{air}, humidity, pressure, and aerosol content to remove atmospheric effects, and assessments of surface radiative properties to correct for emissivity effects. However, correction methods are often instrument (or at least platform) specific and difficult to generalize across sensor and platform types. Few methods exist for correction of ground based remote sensed TIR --- none of which are robust enough to correct irradiances upwelling from rough terrain measured via wide-\gls{fov} (FOV) radiometers. In part, this is due to the fact that until recently, errors inherent in radiometer measurements were large relative to atmospheric effects. However, a new breed of more accurate radiometers and thermal imagers should prompt a critical reevaluation of this assumption.

Atmospheric correction of near-ground remote sensed TIR is subject to a unique set of challenges compared to traditional satellite and aerial platforms. Near-ground and wide-FOV remote sensors have complex, multiple line-of-sight (LOS) geometry - illustrated in figure 2.1 for a downward facing hemispherical radiometer. Surface-sensor geometry varies significantly over the sensor FOV, even when measured close (less than 5m) above the surface. The addition of 3-dimensional surface geometry further amplifies this effect, as some paths may intersect with raised vertical, sloped, and horizontal features. This creates the potential for non-uniform atmospheric effects over the sensor FOV and necessitates a multi-LOS correction to retrieve accurate T\textsubscript{rad}. In effect, with near-ground wide-FOV sensors, surface geometry is non-trivial and must be represented in atmospheric correction routines. In contrast, over a scene retrieved via satellite, spatial viability in surface geometry and LOS angle have a negligible effect on path length. Atmospheric correction routines for satellite retrieved TIR, therefore, assume uniform or single-LOS geometry because the TIR signal passes through a relatively constant volume of atmosphere over the projected sensor FOV, regardless of surface geometry. This greatly increases the complexity of correction routines for near-ground wide-FOV radiometry.

\begin{figure}[!ht]
	\includegraphics[width=\textwidth]{lineofsight}
	\label{lineofsight}
	\caption{Variable path geometry inherent with wide-FOV near-ground sensor visualized over an idealized 2-dimensional urban area.}
\end{figure}

Several multi-LOS atmospheric correction routines have been developed for near-ground TIR: Meier et al., 2011 describes a correction method for oblique angled urban thermography \cite{Meier2011}. Path lengths were calculated for each pixel over the FOV of a tower-mounted thermal imager angled obliquely toward the urban surface. A correction factor was then computed and applied using a radiative transfer code initialized using isothermal, isohumal atmospheric profiles for each time step. Applied over a time-series of images, the result is a continuous atmospherically corrected series of thermal images with each pixel representing a different T\textsubscript{rad}. However, the method uses visual-band images and a GIS database to represent urban geometry for each pixel's LOS - a technique not possible with a pyrgeometer, which returns a single integrated irradiance at each time-step. Moreover, the target instrument operates over a narrow waveband, reducing the magnitude and variance in atmospheric transmission over the sensor response curve. Thus, the method is not directly generalizable to correction TIR as measured via pyrgeometer.  Kotani \& Sugita, 2009 describes a method for correction of wide-FOV (pyrgeometer) TIR Irradiances \cite{Kotani2009a} over planar terrain. However, these methods are limited to narrow-FOV thermal imagers and sensors over planar surfaces respectively. A method which combines Meier et al., 2009's representation of complex surface geometry and Kotani \& Sugita, 2009's broadband hemispherical integration is needed for atmospheric correction of urban TIR measured from a downward facing pyrgeometer. A method to correct hemispherical broadband TIR as measured from a downward facing pyrgeometer needs to combine the two for accurate T\textsubscript{hem} retrieval over rough terrain.

@@

The "rolling lookup-table" method described in this study uses a sensor view model in conjunction with a radiative transfer code to model hemispherical irradiances upwelling from a simplified isothermal 3-dimensional representation of the target study area. In summary, the method (depicted in figure \ref{flow}) uses vertical profiles of measured T\textsubscript{air} and humidity to model at-sensor spectral radiances at 5$^{\circ}$ increments over the sensor FOV for a predefined range of possible T\textsubscript{hem} at each time-step. Spectral directional radiances are convolved by a dome transmittance curve, integrated over the sensor waveband, and weighted for their respective angular view factor. Weighted directional radiances are then integrated over the hemisphere and aggregated into a lookup table (LUT) of modeled irradiance---T\textsubscript{hem} pairings for each timestep, unique to the vertical profile of measured T\textsubscript{air} and humidity. Finally, for each time-step, measured irradiances are matched with the closest modeled irradiances in the associated LUT to return an atmospherically corrected hemispherical surface temperature (T\textsubscript{hem}). This process is repeated at 30 minute intervals to yield a continuous climatology of urban T\textsubscript{hem} for surface urban heat island (sUHI) analysis. The following sections introduce the study area and describe the sensor view modeling, radiative transfer, and post-processing steps of the method.

\begin{figure}[!ht]
	\includegraphics[width=\textwidth]{flow}
	\label{flow}
	\caption{A workflow schematic depicting the input, model, and output-processing steps of a "rolling lookup table method" for hemispherical radiometric surface temperature retrial.}
\end{figure}

@@

As discussed in Section \ref{Atmospheric correction of near-ground TIR}, atmospheric correction of longwave irradiances measured from downward-facing, near-ground, wide-FOV sensors must account for surface geometry - particularly when mounted to view complex surface geometry. Hence, routines to retrieve atmospherically corrected urban T\textsubscript{hem} from upwelling longwave irradiances are inherently site specific. However, it is important to note that although correction magnitudes described in this paper are not generalizable, the correction method described in this paper can readily be adapted to different study sites, pyrgeometer types, and unique surface geometries.

>>>>

\chapter{A method to correct upwelling longwave radiation to estimate hemispherical urban surface temperature}\label{paper1}

\section{Introduction}
Thermal infrared (TIR) remote sensing of land surface temperature (T\textsubscript{surf}) has emerged as a primary research focus in climatology, as researchers seek to better describe spatiotemporal patterns of T\textsubscript{surf} globally and better understand how anthropogenic modification of earth's surface influences land T\textsubscript{surf} and impacts climate at various scales. Over the last two decades, the application of thermal remote sensing to study surface climates has expanded significantly. Thermal remote sensing of earth's surface has applications over a wide range of disciplines: from informing micro-, urban-, and global-scale climate models, to aiding decision making and mitigation praxis with respect to climate change and the \gls{uhi}.

Within urban climatology, a combination of satellite, aerial, and ground-based thermal remote sensors have been integral in elucidating the spatial \cite{Roth1989}, temporal \cite{Peng2012}, and geometric \cite{Voogt1997} effects of the built environment on land T\textsubscript{surf}; in evaluating and partitioning urban surface energy balances \cite{BastiaanssenW.G.M.1998, Yamaguchi2005} and; in characterizations of the relationship between surface and \gls{blayer} air temperatures (T\textsubscript{air}) \cite{Stoll1992}. These advances have been aided by substantial improvements in sensor spatial, spectral, and radiometric resolutions, and by the proliferation of both large-scale public satellite remote sensing campaigns and low-cost aerial and near-ground thermography. However, in spite of it's widespread usage, several questions concerning the use and validity of urban remote thermal remote sensing, first posed in Roth et al. 1989 \cite{Roth1989}, have yet to be sufficiently answered, viz,

@@

\noindent In this paper, we seek to examine question two by introducing and evaluating a method for atmospheric correction of near-ground hemispherical TIR --- measured via \gls{pyrg} --- for hemispherical radiometric temperature (T\textsubscript{hem, r}) retrieval. These measures are common to most urban energy balance assessments and thus constitute a hitherto untapped method for urban T\textsubscript{surf} analysis. A companion paper responds to question one through an analysis of an 8-month climatology of T\textsubscript{hem, r} and derived surface UHI magnitudes (sUHI), to quantify geometric and temporal biases across multiple methods for remote sensing of urban T\textsubscript{surf}.

@@

Although most thermal remote sensors operate within one of the \gls{atmwind}[s] - where atmospheric effects are minimal - virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared \gls{waveband} the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal almost certainly not equal to the ground emitted signal. Spectral radiance received by a sensor at height ($z$) can be described by a function deviating from a Planck curve defined by T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation determined by the difference between Planck curves calculated from T\textsubscript{surf} and ambient T\textsubscript{air}. A radiative transfer code, such as MODTRAN \cite{Berk1987}, can be used to model the effect of the atmosphere on a remote sensed TIR signal. Radiative transfer simulations run in MODTRAN version 4.1 for two path lengths are shown in figure \ref{spectairtsurf}, for spectral radiance emitted from a planar surface at 300 \si{kelvin} through an isothermal atmosphere at 290 \si{\kelvin}, water vapor content of 12 \si{\gram\per\meter\cubed}, and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere \cite{Kantor1962}. At both short and long path lengths, radiance in each band shows some deviation from the ground emitted signal. Larger deviations are observed at longer path lengths, where a significant portion of the resulting signal is emitted from that atmosphere, even in bands with high spectral transmittance. Long path lengths and a less transmissive atmosphere increase the potential for deviation in a remote sensed TIR signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{spectairtsurf}
	\caption{At-sensor spectral directional radiances computed in MODTRAN 4.1 \cite{Berk1987} for short (30 \si{m}) and long (3000 \si{m}) path lengths (z) with Planck curves indicating spectral radiances at T\textsubscript{surf} = 300 \si{K} and T\textsubscript{air} = 290 \si{K}.}
	\label{spectairtsurf}
\end{figure}

Atmospheric effects can lead to differences between the 'true' radiometric T\textsubscript{surf} and the remote sensed T\textsubscript{surf} of over 10 \si{K} for satellite platforms \cite{Cooper1989} and over 6 \si{K} for near-ground sensors \cite{Meier2011}. Moreover, because atmospheric effects are a function of non-uniform and spatiotemporally variant surface and atmospheric properties, their associated errors change depending on instrument type, surface-sensor geometry, study location, and ambient conditions. As intersite and time-continuous analysis is a significant goal of most thermal remote sensed studies (urban or otherwise) these effects cannot be ignored.

Spectral transmission of longwave radiation through a given layer of atmosphere is dependent on total column absorber content (the principal broadband TIR absorbers are H\textsubscript{2}O, CO\textsubscript{2}, and to a lesser extent O\textsubscript{3}, N\textsubscript{2}O, CO, CH\textsubscript{4}, and O\textsubscript{2} \cite{Miskolczi1993}). Holding vertical absorber content constant through a layer of atmosphere, variation in band-by-band TIR transmittance with path length is greatest at urban scales (approximately 1 to 50 \si{\meter}), where transparent spectral bands can quickly become opaque with small changes in path length or absorber content - illustrated in figure \ref{spectransheight}. Thus, transmittance of TIR near the surface is highly dependent on surface-sensor geometry, instrument spectral response, and atmospheric absorber content. Indeed, accurate assessment of atmospheric influence on TIR may be most complex when measured near the surface.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{spectransheight}
	\caption{Spectral transmission of water vapor as a function of height. Run in MODTRAN 4.1 for radiance emitted from a planar surface at 300 \si{\kelvin} through an atmosphere with water vapor content of 8 \si{\gram\per\meter\cubed}. Sampled at heights of 1, 5, 10, 15, 20, 25, and 30 \si{\meter}.}
	\label{spectransheight}
\end{figure}

\subsection{Describing radiation as received by a remote sensor}

Radiation passing through a layer of atmosphere from an emitting surface towards a sensor can be described in a number of ways: \textit{Spectral directional radiance} $R^\uparrow_z (\lambda, \theta, \phi)$, at height $ z $, wavelength $\lambda$ and from a direction defined by viewingzenith angle \(\theta\), and azimuth angle \(\phi\) is commonly written as

\begin{equation}
R^\uparrow_z (\lambda, \theta, \phi) = \tau_\lambda \epsilon_\lambda R^\uparrow_0(\lambda) + (1-\epsilon_\lambda) R^\downarrow_{sky} (\lambda) + (1-\tau_\lambda) R^\uparrow_{atm}(\lambda)
\end{equation}

\noindent where \(\epsilon\)\textsubscript{\( \lambda \)} is spectral surface emissivity, \(\tau\)\textsubscript{\( \lambda \)} is spectral "slab" transmittance through the layer between the emitting surface $( z  = 0) $ and $ z $. Directional radiances upwelling from the atmosphere $R^\uparrow_{atm}$, and the surface $R^\uparrow_0$, and downwelling from the sky $R^\downarrow_{sky}$, can be described spectrally or integrated over a waveband bounded by \(\lambda_1\) and \(\lambda_2\) as

\begin{equation}
R(\theta, \phi) = \bigints_{\lambda_1}^{\lambda_2} R(\lambda,\theta, \phi) ~ d\lambda =\displaystyle\frac{\epsilon_\lambda C_1}{\pi \lambda^5 \left( \exp\left(\cfrac{C_2}{\lambda T}\right)\right)}
\end{equation}

\noindent where C\textsubscript{1} = $ 3.7404 \cdot 10^8 $ $ W\mu^4 m^{-2} $, C\textsubscript{2} = $ 14387 \mu K $, and $T$ is emitter temperature.

Measured by a narrow-FOV sensor mounted at height $ z $, $R^\uparrow_z (\lambda, \theta, \phi)$ passes through an instrument filter (or dome) with spectral transmittance \(\tau_d\), and is integrated over the sensor waveband to yield a \textit{directional radiance} $L_z'$ as 'seen' by the sensor

\begin{equation}
L_z' (\theta, \phi) = \int_{\lambda_1}^{\lambda_2} \tau_d(\lambda) R^\uparrow_z(\lambda) ~ d\lambda
\end{equation}

@@

TIR received by a remote sensor can be related to a surface temperature in a number of ways --- each producing different conceptions of T\textsubscript{surf} from different instrument and sensor types. As such, the term "surface temperature" with respect to a remote sensed TIR is vague and can refer to several definitions of "surface" and "temperature". Thus, proper terminology must be attached to land T\textsubscript{surf} inferred from TIR. Definitions and nomenclature conventions for multiple methods for T\textsubscript{surf} retrieval are discussed at length in Norman \& Becker, (1995) \cite{Norman1995}.

 Irradiance $L_z$ received by a broadband hemispherical sensor (such as a pyrgeometer), can be used to infer a \textit{hemispherical brightness temperature} T\textsubscript{hem, b} through an inversion of the Stefan-Boltzmann law,

\begin{equation}
\label{stefb1}
T_{hem,~ b} = \sqrt[4]{\frac{L_z}{\overline{r}\sigma}}
\end{equation}

@@

\begin{equation}
\label{meansens}
\overline{r} = \cfrac{\int R(\lambda) ~ r(\lambda)~d\lambda}{\int R(\lambda) ~ d\lambda}
\end{equation}

\noindent with $ R(\lambda) $ computed from a Planck function at an approximated emitter temperature.

A \textit{directional brightness temperature} T\textsubscript{bright} $(\theta, \phi)$ from some viewing able described $\theta$ and $\phi$ by can be inferred from directional radiance via equation \ref{stefb1} by replacing $ L_z $ with $L_z'$ multiplied by a constant. This method is commonly used to infer T\textsubscript{bright} $(\theta, \phi)$ from infrared thermometers (IRT) operating over the atmospheric window - where atmospheric effects are minimal and T\textsubscript{bright} is a reasonably accurate approximation of T\textsubscript{surf}. However, constants must be calibrated for the range of expected T\textsubscript{surf} as the relationship between $ L_z $ and $L_z'$  is not perfectly linear with respect to emitter temperature.

Inversions of uncorrected $ L_z $ or \textbf{$L_z'$} yield a temperature equal to that of a blackbody emitting the same amount of radiation as detected by the sensor. Since $ L_z $ is unlikely to be equal to $ L_0 $ and, by extension,  $L_z'$ is unlikely to be equal to $L_0'$, T\textsubscript{hem, b} at $ z = 0 $ and T\textsubscript{hem, b} at $ z $ often show significant deviation based on sensor characteristics, ambient conditions, and surface-sensor geometry. Hence, T\textsubscript{bright} and T\textsubscript{hem, b} are generally considered only a rough approximation representation of radiometric, kinetic, or thermodynamic T\textsubscript{surf}.

To retrieve a more accurate estimation of the 'true' T\textsubscript{surf}, the same inversions can be applied to TIR measurements after correction for atmospheric effects (e.g. modification of the remote sensed TIR signal to represent the same signal at $ z = 0 $ emitted from a homogeneous, isothermal, blackbody emitter) to yield a \textit{directional radiometric surface temperature} T\textsubscript{rad} from atmospheric corrected directional radiances and a \textit{hemispherical radiometric surface temperature} T\textsubscript{hem, r} from atmospherically corrected irradiances. T\textsubscript{rad} and T\textsubscript{hem, r} provide a better approximation of the ‘true’ T\textsubscript{surf} by representing the temperature at which emitting surfaces are radiating, integrated over the sensor FOV.

@@

A large number of correction routines have been developed to remove atmospheric and emissivity effects from aerial and satellite TIR signals and derive accurate T\textsubscript{rad}. Methods range from simple mono- \cite{Qin2001} and split-window \cite{Wan1996} routines for single- and multi-channel remote sensors, to schemes that integrate a radiative transfer code to isolate the surface emitted signal from interfering signals. Boundary conditions are standard across most correction methods: generally requiring vertical profiles of T\textsubscript{air}, humidity, pressure, and aerosol content to remove atmospheric effects, and surface radiative properties to correct for emissivity effects. However, correction methods are often instrument (or, at the very least, least platform) specific and difficult to generalize across sensor and platform types. Few methods exist for correction of ground based remote sensed TIR --- none of which are robust enough to correct irradiances measured from a near-ground wide-\gls{fov} (FOV) radiometer mounted to view rough terrain.

%In part, this is due to the fact that until recently, errors inherent in radiometer measurements were large relative to atmospheric effects. However, a new breed of more accurate radiometers and thermal imagers should prompt a critical reevaluation of this assumption.

Atmospheric correction of near-ground remote sensed TIR is subject to a unique set of challenges compared to traditional satellite and aerial platforms. Wide-FOV remote sensors have complex, multiple line-of-sight (LOS) path length geometries - illustrated in Figure \ref{lineofsight} for a downward facing pyrgeometer. Surface-sensor geometry varies significantly over the sensor FOV as some path lengths intersect with raised vertical, sloped, and horizontal features. This creates the potential for non-uniform atmospheric effects over the sensor FOV and necessitates a multi-LOS correction to retrieve accurate T\textsubscript{hem, r}. In effect, with near-ground wide-FOV sensors, surface geometry is non-trivial and must be represented in atmospheric correction routines. In contrast, over a scene retrieved via satellite, spatial viability in surface geometry and LOS angle have a negligible effect on path length. Atmospheric correction routines for satellite retrieved TIR, therefore, assume uniform or single-LOS geometry because the TIR signal passes through a relatively constant volume of atmosphere over the projected sensor FOV, regardless of surface geometry.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{lineofsight}
	\caption{Variable path geometry inherent with wide-FOV near-ground sensor visualized over an idealized 2-dimensional urban area.}
	\label{lineofsight}
\end{figure}

Several multi-LOS correction routines have been developed for to remove atmospheric effects on near-ground remote sensed TIR: Meier et al., 2011 describes a correction method for oblique angled thermal imagery of urban terrain \cite{Meier2011}. In the method, spatially distributed LOS geometries were calculated by linking each image pixel to the corresponding 3-d coordinates of its viewpoint on a digital building model (DBM). Path lengths were then calculated as the distance between each pixel's corresponding location on the DBM and the sensor represented as the vanishing point of a 3-dimensional pyramidic projection from the sensor's location in the DBM. A pixel-by-pixel correction was then applied to remove atmospheric effects and retrieve T\textsubscript{rad} for each pixel at 30 minute intervals, resulting in a time-continuous climatology of urban T\textsubscript{rad}. However, the method uses thermal images in conjunction with a DBM to calculate path length geometries for each pixel's LOS - a technique not possible with a pyrgeometer, which returns a single integrated value over the sensor FOV. Moreover, the target instrument operates over a narrow waveband with relatively uniform spectral sensor response, reducing the magnitude and variance in atmospheric transmission over the sensor response curve. Thus, the method is not directly generalizable to correct TIR measured via pyrgeometer.

Kotani \& Sugita, 2009 describes a method for correction of wide-FOV (pyrgeometer) TIR irradiances \cite{Kotani2009a} over a homogeneous planar surface. In this method, path lengths were calculated for six sensor heights. Radiances were then modeled using LOWTRAN initialized at $5^{\circ}$ intervals and integrated over the hemisphere to retrieve irradiances for a suite of T\textsubscript{surf}, and ambient T\textsubscript{air} and humidities. The resulting lookup table (LUT) of values is then used to correct $L_z$ and quantify atmospheric effects on remote sensed $L_z$ measured from several sensor heights. Methods outlined in Meier et al., 2011 and Kotani \& Sugita, 2009 are limited to narrow-FOV thermal imagers and planar terrain respectively. A method which combines Meier et al., 2011's representation of complex surface geometry and Kotani \& Sugita, 2009's broadband hemispherical integration is needed for atmospheric correction of urban TIR measured via downward facing pyrgeometer.

@@

The "rolling lookup-table" method described in this study uses a sensor view model in conjunction with a radiative transfer code to model hemispherical irradiances upwelling from a simplified isothermal 3-dimensional representation of the urban surface. In summary, the method (depicted in Figure \ref{flow}) uses vertical profiles of measured T\textsubscript{air} and humidity to model at-sensor spectral radiances at 5$^{\circ}$ increments over the sensor FOV for a predetermined range of possible T\textsubscript{hem, r} at each time-step. Spectral directional radiances are convolved by a dome transmittance curve, integrated over the sensor waveband, and weighted for their respective angular view factor. Weighted directional radiances are then integrated over the hemisphere and aggregated into a LUT of modeled irradiance - T\textsubscript{hem, r} pairings for each time step, unique to the vertical profile of measured T\textsubscript{air} and humidity. Finally, for each time step, measured irradiances are matched with the closest modeled irradiances in the LUT to return an atmospherically corrected radiometric hemispherical surface temperature. This process is repeated at 30 minute intervals to yield a continuous climatology of urban T\textsubscript{hem, r} for surface urban heat island (sUHI) analysis. The following sections introduce the study area for which the method was developed and describe the sensor view model, radiative transfer, and post-processing steps of the correction method.

\begin{figure}[!ht]
	\includegraphics[width=\textwidth]{flow}
	\caption{A workflow schematic depicting the input, model, and output-processing steps of a "rolling lookup table method" for hemispherical radiometric surface temperature retrial.}
	\label{flow}
\end{figure}

@@

As discussed in section \ref{Atmospheric correction of near-ground TIR}, atmospheric correction of longwave irradiances measured from downward-facing, near-ground, wide-FOV sensors must account for complex surface geometry. Thus, routines to retrieve atmospherically corrected urban T\textsubscript{hem, r} from upwelling longwave irradiances are inherently site specific. However, it is important to note that although correction \textit{magnitudes} described in this paper are not necessarily generalizable, the correction \textit{method} described in this paper can readily be adapted to different study sites, sensor types, and unique surface geometries.
